---
title: "CytoExploreR-Docker"
author: "Dillon Hammill"
date: '2023-03-10'
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Docker development environment for CytoExploreR Version 2.0.0

This repository contains a dockerfile and associated build instructions to launch a CytoExploreR v2.0.0 RStudio environment for testing, development or benchmarking.

The pre-built docker images are available for download (amd64 platform) from docker hub: `docker pull dhammill/cytoexplorer-devel:v2.0.0`.

This docker image contains: 

1. Ubuntu 18.04 
2. FFTW 
3. FIt-SNE executable 
4. Open-source cytoverse packages 
5. CytoExploreRData datasets 
6. CytoExploreR 
7. tidyverse packages 
8. Miniconda virtual environment ("cytoexplorer")

# Build Docker image locally

1.  Clone this repository to obtain a local copy: `git clone https://github.com/djhammill/CytoExploreR-Docker.git`

2.  From the terminal/command prompt build and tag the docker image: `docker build -t cytoexplorer-devel:v2.0.0 .`

3.  Check image has been built successfully: `docker image ls`

# Start Docker container & mount local drives

1.  Either pull down pre-built image from Docker Hub (`docker pull dhammill/cytoexplorer-devel:v2.0.0`) or build image locally as above.

2.  Run the CytoExploreR version 2.0.0 docker image inside a container and mount directory (edit /path/to/mount). Remove `dhammill` below if image was built locally.
```{r, eval = FALSE}
docker run --rm -dit --mount type=bind,source=/path/to/mount,destination=/home/rstudio/project -p 8787:8787 -e PASSWORD=cytoexplorer dhammill/cytoexplorer-devel:v2.0.0
```
